---
title: "Histology & immunohistochemistry analysis"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---

Jan Homolak. May 2025.

The aim of this notebook is to compare pathoscores and cell staining obtained by immunohistochemistry between DMSO (vehicle)– and Terfenadine-treated mice, with or without exposure to S. Tm.

## Load Required Libraries

```{r}
library(tidyverse)
library(ggplot2)
library(readxl)
library(scales)
library(emmeans)
library(lme4)
```

## Set Path and Color Palettes

```{r}
#Set path to your data folder
path <- c("C:/Users/Korisnik/Desktop/Experiments/Experiments/Experiments 2024/Anne/Anne Histo/final/")

#Color palettes for plots
colorlist_orange <- c("#EE7600", "#EE7600")
colorlist_grey <- c("#84838B", "#84838B")

```

## Pathoscore Analysis: Infection Group

```{r}
#Load data for infection group
pathoscore_data <- read_excel(paste0(path, "Fig_4.xlsx"), sheet = "4I") %>%
filter(Infection == "infection")

#Fit GLMM
model <- glmer(Pathoscore + 0.01 ~ Treatment + (1 | Mouse),
data = pathoscore_data,
family = Gamma(link = "log"),
control = glmerControl(optimizer = "bobyqa"))

#plot(model)

#Estimated marginal means and pairwise comparisons
data_model <- emmeans(model, specs = pairwise ~ Treatment, type = "response")$emmeans %>% as.data.frame()
contrast_results <- emmeans(model, specs = pairwise ~ Treatment, adjust = "Holm")$contrasts %>%
summary(infer = TRUE) %>% as.data.frame()
contrast_results <- contrast_results %>%
  mutate(
    p_value = round(p.value, 4),
    sig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE            ~ "ns"
    )
  )
```
## Plot: Pathoscore (Infection Group)

```{r}
plot_infection <- ggplot(data_model, aes(Treatment, response)) +
  geom_point(data = pathoscore_data, 
             aes(Treatment, Pathoscore, color = Treatment), 
             position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.3),
             alpha = 0.5,
             size = 3,
             show.legend = FALSE) +
  geom_point(size = 3, color = "firebrick3", shape = 3) +
  geom_errorbar(aes(ymin = response - SE, ymax = response + SE), 
                color = "firebrick3", width = 0, linewidth = 0.5) +
  theme_light() + 
  ylab("Pathoscore") + 
  ggtitle("Infection Group") +
  geom_text(data = contrast_results, 
            aes(x = 1.5, y = 2.5, label = paste("p =", sig)), 
            size = 4, vjust = -1) +
  scale_y_continuous(breaks = c(0, 4, 9, 13)) +
  geom_rect(ymin = 0, ymax = 4, xmin = -Inf, xmax = 0.7, 
            fill = "grey", alpha = 0.2, color = "black") +
  geom_rect(ymin = 4, ymax = 9, xmin = -Inf, xmax = 0.7, 
            fill = "grey", alpha = 0.2, color = "black") +
  geom_rect(ymin = 9, ymax = 13, xmin = -Inf, xmax = 0.7, 
            fill = "grey", alpha = 0.2, color = "black") +
    ggplot2::annotate("text", x = 0.55, y = 2, label = "No\ninflammation", color = "black", size = 3, angle = 90) +
  ggplot2::annotate("text", x = 0.55, y = 6.5, label = "Mild\ninflammation", color = "black", size = 3, angle = 90) +
  ggplot2::annotate("text", x = 0.55, y = 11, label = "Severe\ninflammation", color = "black", size = 3, angle = 90) +
  scale_color_manual(values = c("#EE7600", "#EE7600"))

plot_infection
```

## Pathoscore Analysis: No Infection Group

```{r}
#Load data for no infection group
pathoscore_data <- read_excel(paste0(path, "Fig_4.xlsx"), sheet = "4I") %>%
filter(Infection == "no infection")

#Fit GLMM
model <- glmer(Pathoscore + 0.01 ~ Treatment + (1 | Mouse),
data = pathoscore_data,
family = Gamma(link = "log"),
control = glmerControl(optimizer = "bobyqa"))

#plot(model)

#Estimated marginal means and pairwise comparisons
data_model <- emmeans(model, specs = pairwise ~ Treatment, type = "response")$emmeans %>% as.data.frame()
contrast_results <- emmeans(model, specs = pairwise ~ Treatment, adjust = "Holm")$contrasts %>%
summary(infer = TRUE) %>% as.data.frame()
contrast_results <- contrast_results %>%
  mutate(
    p_value = round(p.value, 4),
    sig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE            ~ "ns"
    )
  )
```
## Plot: Pathoscore (No Infection Group)

```{r}
plot_no_infection <- ggplot(data_model, aes(Treatment, response)) +
  geom_point(data = pathoscore_data, 
             aes(Treatment, Pathoscore, color = Treatment), 
             position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.3),
             alpha = 0.5,
             size = 3,
             show.legend = FALSE) +
  geom_point(size = 3, color = "firebrick3", shape = 3) +
  geom_errorbar(aes(ymin = response - SE, ymax = response + SE), 
                color = "firebrick3", width = 0, linewidth = 0.5) +
  theme_light() + 
  ylab("Pathoscore") + 
  ggtitle("Infection Group") +
  geom_text(data = contrast_results, 
            aes(x = 1.5, y = 2.5, label = paste("p =", sig)), 
            size = 4, vjust = -1) +
  scale_y_continuous(breaks = c(0, 4, 9, 13)) +
  geom_rect(ymin = 0, ymax = 4, xmin = -Inf, xmax = 0.7, 
            fill = "grey", alpha = 0.2, color = "black") +
  geom_rect(ymin = 4, ymax = 9, xmin = -Inf, xmax = 0.7, 
            fill = "grey", alpha = 0.2, color = "black") +
  geom_rect(ymin = 9, ymax = 13, xmin = -Inf, xmax = 0.7, 
            fill = "grey", alpha = 0.2, color = "black") +
  ggplot2::annotate("text", x = 0.55, y = 2, label = "No\ninflammation", color = "black", size = 3, angle = 90) +
  ggplot2::annotate("text", x = 0.55, y = 6.5, label = "Mild\ninflammation", color = "black", size = 3, angle = 90) +
  ggplot2::annotate("text", x = 0.55, y = 11, label = "Severe\ninflammation", color = "black", size = 3, angle = 90) +
  scale_color_manual(values = c("#84838B", "#84838B"))

plot_no_infection
```
## CD4 IHC Analysis

```{r}
#Load IHC data (CD4, infection group)
ihc_data <- read_excel(paste0(path, "Fig_S1.xlsx"), sheet = "S1F") %>%
filter(staining == "CD4" & infection == "infection")

#Fit GLMM for CD4+ cells
model <- glmer(num_pos_per_mm2 ~ treatment + (1 | animal),
data = ihc_data,
family = Gamma(link = "log"),
control = glmerControl(optimizer = "bobyqa"))

#plot(model)

#Estimated marginal means and pairwise comparisons
data_model <- emmeans(model, specs = pairwise ~ treatment, type = "response")$emmeans %>% as.data.frame()
contrast_results <- emmeans(model, specs = pairwise ~ treatment, adjust = "Holm")$contrasts %>%
summary(infer = TRUE) %>% as.data.frame()
contrast_results <- contrast_results %>%
  mutate(
    p_value = round(p.value, 4),
    sig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE            ~ "ns"
    )
  )
```

## Plot: CD4 IHC (Infection Group)

```{r}
plot_cd4_inf <- ggplot(data_model, aes(treatment, response)) +
geom_point(data = ihc_data, aes(treatment, num_pos_per_mm2, color = treatment),
position = position_jitterdodge(jitter.width = 0.3), alpha = 0.5, size = 3) +
geom_point(size = 3, color = "firebrick3", shape = 3) +
geom_errorbar(aes(ymin = response - SE, ymax = response + SE), color = "firebrick3", width = 0, linewidth = 0.5) +
theme_light() + ylab(expression("Positive cells per mm"^2)) + ggtitle("CD4+ Cells") +
geom_text(data = contrast_results, aes(x = 1.5, y = 10, label = paste("p =", sig)), size = 4, vjust = -1) +
scale_y_log10()+
scale_color_manual(values = c("#EE7600", "#EE7600"))

plot_cd4_inf
```
## Plot: CD4 IHC (No Infection Group)

```{r}
#Load IHC data (CD4, no infection group)
ihc_data <- read_excel(paste0(path, "Fig_S1.xlsx"), sheet = "S1F") %>%
filter(staining == "CD4" & infection == "no infection")

#Fit GLMM for CD4+ cells
model <- glmer(num_pos_per_mm2 ~ treatment + (1 | animal),
data = ihc_data,
family = Gamma(link = "log"),
control = glmerControl(optimizer = "bobyqa"))

#plot(model)

#Estimated marginal means and pairwise comparisons
data_model <- emmeans(model, specs = pairwise ~ treatment, type = "response")$emmeans %>% as.data.frame()
contrast_results <- emmeans(model, specs = pairwise ~ treatment, adjust = "Holm")$contrasts %>%
summary(infer = TRUE) %>% as.data.frame()
contrast_results <- contrast_results %>%
  mutate(
    p_value = round(p.value, 4),
    sig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE            ~ "ns"
    )
  )
```



```{r}
plot_cd4_no_inf <- ggplot(data_model, aes(treatment, response)) +
geom_point(data = ihc_data, aes(treatment, num_pos_per_mm2, color = treatment),
position = position_jitterdodge(jitter.width = 0.3), alpha = 0.5, size = 3) +
geom_point(size = 3, color = "firebrick3", shape = 3) +
geom_errorbar(aes(ymin = response - SE, ymax = response + SE), color = "firebrick3", width = 0, linewidth = 0.5) +
theme_light() + ylab(expression("Positive cells per mm"^2)) + ggtitle("CD4+ Cells") +
geom_text(data = contrast_results, aes(x = 1.5, y = 10, label = paste("p =", sig)), size = 4, vjust = -1) +
scale_y_log10()+
scale_color_manual(values = c("#84838B", "#84838B"))

plot_cd4_no_inf
```






## CD11b IHC Analysis

```{r}
#Load IHC data (CD11b, infection group)
ihc_data <- read_excel(paste0(path, "Fig_S1.xlsx"), sheet = "S1B") %>%
filter(staining == "CD11b" & infection == "infection")

#Fit GLMM for CD11b cells
model <- glmer(num_pos_per_mm2 ~ treatment + (1 | animal),
data = ihc_data,
family = Gamma(link = "log"),
control = glmerControl(optimizer = "bobyqa"))

#plot(model)

#Estimated marginal means and pairwise comparisons
data_model <- emmeans(model, specs = pairwise ~ treatment, type = "response")$emmeans %>% as.data.frame()
contrast_results <- emmeans(model, specs = pairwise ~ treatment, adjust = "Holm")$contrasts %>%
summary(infer = TRUE) %>% as.data.frame()
contrast_results <- contrast_results %>%
  mutate(
    p_value = round(p.value, 4),
    sig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE            ~ "ns"
    )
  )
```

## Plot: CD11b IHC (Infection Group)

```{r}
plot_cd11b_inf <- ggplot(data_model, aes(treatment, response)) +
geom_point(data = ihc_data, aes(treatment, num_pos_per_mm2, color = treatment),
position = position_jitterdodge(jitter.width = 0.3), alpha = 0.5, size = 3) +
geom_point(size = 3, color = "firebrick3", shape = 3) +
geom_errorbar(aes(ymin = response - SE, ymax = response + SE), color = "firebrick3", width = 0, linewidth = 0.5) +
theme_light() + ylab(expression("Positive cells per mm"^2)) + ggtitle("CD11b Cells") +
geom_text(data = contrast_results, aes(x = 1.5, y = 10, label = paste("p =", sig)), size = 4, vjust = -1) +
scale_y_log10()+
scale_color_manual(values = c("#EE7600", "#EE7600"))

plot_cd11b_inf
```
## Plot: CD11b IHC (No Infection Group)

```{r}
#Load IHC data (CD11b, no infection group)
ihc_data <- read_excel(paste0(path, "Fig_S1.xlsx"), sheet = "S1B") %>%
filter(staining == "CD11b" & infection == "no infection")

#Fit GLMM for CD11b cells
model <- glmer(num_pos_per_mm2 ~ treatment + (1 | animal),
data = ihc_data,
family = Gamma(link = "log"),
control = glmerControl(optimizer = "bobyqa"))

#plot(model)

#Estimated marginal means and pairwise comparisons
data_model <- emmeans(model, specs = pairwise ~ treatment, type = "response")$emmeans %>% as.data.frame()
contrast_results <- emmeans(model, specs = pairwise ~ treatment, adjust = "Holm")$contrasts %>%
summary(infer = TRUE) %>% as.data.frame()
contrast_results <- contrast_results %>%
  mutate(
    p_value = round(p.value, 4),
    sig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE            ~ "ns"
    )
  )
```



```{r}
plot_cd11b_no_inf <- ggplot(data_model, aes(treatment, response)) +
geom_point(data = ihc_data, aes(treatment, num_pos_per_mm2, color = treatment),
position = position_jitterdodge(jitter.width = 0.3), alpha = 0.5, size = 3) +
geom_point(size = 3, color = "firebrick3", shape = 3) +
geom_errorbar(aes(ymin = response - SE, ymax = response + SE), color = "firebrick3", width = 0, linewidth = 0.5) +
theme_light() + ylab(expression("Positive cells per mm"^2)) + ggtitle("CD11b Cells") +
geom_text(data = contrast_results, aes(x = 1.5, y = 10, label = paste("p =", sig)), size = 4, vjust = -1) +
scale_y_log10()+
scale_color_manual(values = c("#84838B", "#84838B"))

plot_cd11b_no_inf
```

## CD11c IHC Analysis

```{r}
#Load IHC data (CD11c, no infection group)
ihc_data <- read_excel(paste0(path, "Fig_S1.xlsx"), sheet = "S1C") %>%
filter(staining == "CD11c" & infection == "infection")

#Fit GLMM for CD11c cells
model <- glmer(num_pos_per_mm2 ~ treatment + (1 | animal),
data = ihc_data,
family = Gamma(link = "log"),
control = glmerControl(optimizer = "bobyqa"))

#plot(model)

#Estimated marginal means and pairwise comparisons
data_model <- emmeans(model, specs = pairwise ~ treatment, type = "response")$emmeans %>% as.data.frame()
contrast_results <- emmeans(model, specs = pairwise ~ treatment, adjust = "Holm")$contrasts %>%
summary(infer = TRUE) %>% as.data.frame()
contrast_results <- contrast_results %>%
  mutate(
    p_value = round(p.value, 4),
    sig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE            ~ "ns"
    )
  )
```

## Plot: CD11c IHC (Infection Group)

```{r}
plot_cd11c_inf <- ggplot(data_model, aes(treatment, response)) +
geom_point(data = ihc_data, aes(treatment, num_pos_per_mm2, color = treatment),
position = position_jitterdodge(jitter.width = 0.3), alpha = 0.5, size = 3) +
geom_point(size = 3, color = "firebrick3", shape = 3) +
geom_errorbar(aes(ymin = response - SE, ymax = response + SE), color = "firebrick3", width = 0, linewidth = 0.5) +
theme_light() + ylab(expression("Positive cells per mm"^2)) + ggtitle("CD11c Cells") +
geom_text(data = contrast_results, aes(x = 1.5, y = 10, label = paste("p =", sig)), size = 4, vjust = -1) +
scale_y_log10()+
scale_color_manual(values = c("#EE7600", "#EE7600"))

plot_cd11c_inf
```
```{r}
#Load IHC data (CD11c, no infection group)
ihc_data <- read_excel(paste0(path, "Fig_S1.xlsx"), sheet = "S1C") %>%
filter(staining == "CD11c" & infection == "no infection")

#Fit GLMM for CD11c cells
model <- glmer(num_pos_per_mm2 ~ treatment + (1 | animal),
data = ihc_data,
family = Gamma(link = "log"),
control = glmerControl(optimizer = "bobyqa"))

#plot(model)

#Estimated marginal means and pairwise comparisons
data_model <- emmeans(model, specs = pairwise ~ treatment, type = "response")$emmeans %>% as.data.frame()
contrast_results <- emmeans(model, specs = pairwise ~ treatment, adjust = "Holm")$contrasts %>%
summary(infer = TRUE) %>% as.data.frame()
contrast_results <- contrast_results %>%
  mutate(
    p_value = round(p.value, 4),
    sig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE            ~ "ns"
    )
  )
```



```{r}
plot_cd11c_no_inf <- ggplot(data_model, aes(treatment, response)) +
geom_point(data = ihc_data, aes(treatment, num_pos_per_mm2, color = treatment),
position = position_jitterdodge(jitter.width = 0.3), alpha = 0.5, size = 3) +
geom_point(size = 3, color = "firebrick3", shape = 3) +
geom_errorbar(aes(ymin = response - SE, ymax = response + SE), color = "firebrick3", width = 0, linewidth = 0.5) +
theme_light() + ylab(expression("Positive cells per mm"^2)) + ggtitle("CD11c Cells") +
geom_text(data = contrast_results, aes(x = 1.5, y = 10, label = paste("p =", sig)), size = 4, vjust = -1) +
scale_y_log10()+
scale_color_manual(values = c("#84838B", "#84838B"))

plot_cd11c_no_inf
```




## F4/80 IHC Analysis

```{r}
#Load IHC data (F4/80, infection group)
ihc_data <- read_excel(paste0(path, "Fig_S1.xlsx"), sheet = "S1D") %>%
filter(staining == "F480" & infection == "infection")

#Fit GLMM for F4/80 cells
model <- glmer(num_pos_per_mm2 ~ treatment + (1 | animal),
data = ihc_data,
family = Gamma(link = "log"),
control = glmerControl(optimizer = "bobyqa"))

#plot(model)

#Estimated marginal means and pairwise comparisons
data_model <- emmeans(model, specs = pairwise ~ treatment, type = "response")$emmeans %>% as.data.frame()
contrast_results <- emmeans(model, specs = pairwise ~ treatment, adjust = "Holm")$contrasts %>%
summary(infer = TRUE) %>% as.data.frame()
contrast_results <- contrast_results %>%
  mutate(
    p_value = round(p.value, 4),
    sig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE            ~ "ns"
    )
  )
```

## Plot: F4/80 IHC (Infection Group)

```{r}
plot_f480_inf <- ggplot(data_model, aes(treatment, response)) +
geom_point(data = ihc_data, aes(treatment, num_pos_per_mm2, color = treatment),
position = position_jitterdodge(jitter.width = 0.3), alpha = 0.5, size = 3) +
geom_point(size = 3, color = "firebrick3", shape = 3) +
geom_errorbar(aes(ymin = response - SE, ymax = response + SE), color = "firebrick3", width = 0, linewidth = 0.5) +
theme_light() + ylab(expression("Positive cells per mm"^2)) + ggtitle("F4/80 Cells") +
geom_text(data = contrast_results, aes(x = 1.5, y = 10, label = paste("p =", sig)), size = 4, vjust = -1) +
scale_y_log10()+
scale_color_manual(values = c("#EE7600", "#EE7600"))

plot_f480_inf

```
```{r}
#Load IHC data (F4/80, no infection group)
ihc_data <- read_excel(paste0(path, "Fig_S1.xlsx"), sheet = "S1D") %>%
filter(staining == "F480" & infection == "no infection")

#Fit GLMM for F4/80 cells
model <- glmer(num_pos_per_mm2 ~ treatment + (1 | animal),
data = ihc_data,
family = Gamma(link = "log"),
control = glmerControl(optimizer = "bobyqa"))

#plot(model)

#Estimated marginal means and pairwise comparisons
data_model <- emmeans(model, specs = pairwise ~ treatment, type = "response")$emmeans %>% as.data.frame()
contrast_results <- emmeans(model, specs = pairwise ~ treatment, adjust = "Holm")$contrasts %>%
summary(infer = TRUE) %>% as.data.frame()
contrast_results <- contrast_results %>%
  mutate(
    p_value = round(p.value, 4),
    sig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE            ~ "ns"
    )
  )
```



```{r}
plot_f480_no_inf <- ggplot(data_model, aes(treatment, response)) +
geom_point(data = ihc_data, aes(treatment, num_pos_per_mm2, color = treatment),
position = position_jitterdodge(jitter.width = 0.3), alpha = 0.5, size = 3) +
geom_point(size = 3, color = "firebrick3", shape = 3) +
geom_errorbar(aes(ymin = response - SE, ymax = response + SE), color = "firebrick3", width = 0, linewidth = 0.5) +
theme_light() + ylab(expression("Positive cells per mm"^2)) + ggtitle("F4/80 Cells") +
geom_text(data = contrast_results, aes(x = 1.5, y = 10, label = paste("p =", sig)), size = 4, vjust = -1) +
scale_y_log10()+
scale_color_manual(values = c("#84838B", "#84838B"))

plot_f480_no_inf
```

## B220 IHC Analysis

```{r}
#Load IHC data (B220, infection group)
ihc_data <- read_excel(paste0(path, "Fig_S1.xlsx"), sheet = "S1E") %>%
filter(staining == "B220" & infection == "infection")

#Fit GLMM for B220 cells
model <- glmer(num_pos_per_mm2 ~ treatment + (1 | animal),
data = ihc_data,
family = Gamma(link = "log"),
control = glmerControl(optimizer = "bobyqa"))

#plot(model)

#Estimated marginal means and pairwise comparisons
data_model <- emmeans(model, specs = pairwise ~ treatment, type = "response")$emmeans %>% as.data.frame()
contrast_results <- emmeans(model, specs = pairwise ~ treatment, adjust = "Holm")$contrasts %>%
summary(infer = TRUE) %>% as.data.frame()
contrast_results <- contrast_results %>%
  mutate(
    p_value = round(p.value, 4),
    sig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE            ~ "ns"
    )
  )
```

## Plot: B220 IHC (Infection Group)

```{r}
plot_b220_inf <- ggplot(data_model, aes(treatment, response)) +
geom_point(data = ihc_data, aes(treatment, num_pos_per_mm2, color = treatment),
position = position_jitterdodge(jitter.width = 0.3), alpha = 0.5, size = 3) +
geom_point(size = 3, color = "firebrick3", shape = 3) +
geom_errorbar(aes(ymin = response - SE, ymax = response + SE), color = "firebrick3", width = 0, linewidth = 0.5) +
theme_light() + ylab(expression("Positive cells per mm"^2)) + ggtitle("B220 Cells") +
geom_text(data = contrast_results, aes(x = 1.5, y = 10, label = paste("p =", sig)), size = 4, vjust = -1) +
scale_y_log10()+
scale_color_manual(values = c("#EE7600", "#EE7600"))

plot_b220_inf
```
```{r}
#Load IHC data (B220, no infection group)
ihc_data <- read_excel(paste0(path, "Fig_S1.xlsx"), sheet = "S1E") %>%
filter(staining == "B220" & infection == "no infection")

#Fit GLMM for B220 cells
model <- glmer(num_pos_per_mm2 + 0.01 ~ treatment + (1 | animal),
data = ihc_data,
family = Gamma(link = "log"),
control = glmerControl(optimizer = "bobyqa"))

#plot(model)

#Estimated marginal means and pairwise comparisons
data_model <- emmeans(model, specs = pairwise ~ treatment, type = "response")$emmeans %>% as.data.frame()
contrast_results <- emmeans(model, specs = pairwise ~ treatment, adjust = "Holm")$contrasts %>%
summary(infer = TRUE) %>% as.data.frame()
contrast_results <- contrast_results %>%
  mutate(
    p_value = round(p.value, 4),
    sig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE            ~ "ns"
    )
  )
```



```{r}
plot_b220_no_inf <- ggplot(data_model, aes(treatment, response)) +
geom_point(data = ihc_data, aes(treatment, num_pos_per_mm2, color = treatment),
position = position_jitterdodge(jitter.width = 0.3), alpha = 0.5, size = 3) +
geom_point(size = 3, color = "firebrick3", shape = 3) +
geom_errorbar(aes(ymin = response - SE, ymax = response + SE), color = "firebrick3", width = 0, linewidth = 0.5) +
theme_light() + ylab(expression("Positive cells per mm"^2)) + ggtitle("B220 Cells") +
geom_text(data = contrast_results, aes(x = 1.5, y = 10, label = paste("p =", sig)), size = 4, vjust = -1) +
scale_y_log10()+
scale_color_manual(values = c("#84838B", "#84838B"))

plot_b220_no_inf
```

## CD8 IHC Analysis

```{r}
#Load IHC data (CD8, infection group)
ihc_data <- read_excel(paste0(path, "Fig_S1.xlsx"), sheet = "S1G") %>%
filter(staining == "CD8" & infection == "infection")

#Fit GLMM for CD8 cells
model <- glmer(num_pos_per_mm2 ~ treatment + (1 | animal),
data = ihc_data,
family = Gamma(link = "log"),
control = glmerControl(optimizer = "bobyqa"))

#plot(model)

#Estimated marginal means and pairwise comparisons
data_model <- emmeans(model, specs = pairwise ~ treatment, type = "response")$emmeans %>% as.data.frame()
contrast_results <- emmeans(model, specs = pairwise ~ treatment, adjust = "Holm")$contrasts %>%
summary(infer = TRUE) %>% as.data.frame()
contrast_results <- contrast_results %>%
  mutate(
    p_value = round(p.value, 4),
    sig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE            ~ "ns"
    )
  )
```

## Plot: CD8 IHC (Infection Group)

```{r}
plot_cd8_inf <- ggplot(data_model, aes(treatment, response)) +
geom_point(data = ihc_data, aes(treatment, num_pos_per_mm2, color = treatment),
position = position_jitterdodge(jitter.width = 0.3), alpha = 0.5, size = 3) +
geom_point(size = 3, color = "firebrick3", shape = 3) +
geom_errorbar(aes(ymin = response - SE, ymax = response + SE), color = "firebrick3", width = 0, linewidth = 0.5) +
theme_light() + ylab(expression("Positive cells per mm"^2)) + ggtitle("CD8 Cells") +
geom_text(data = contrast_results, aes(x = 1.5, y = 10, label = paste("p =", sig)), size = 4, vjust = -1) +
scale_y_log10()+
scale_color_manual(values = c("#EE7600", "#EE7600"))

plot_cd8_inf
```
```{r}
#Load IHC data (CD8, infection group)
ihc_data <- read_excel(paste0(path, "Fig_S1.xlsx"), sheet = "S1G") %>%
filter(staining == "CD8" & infection == "no infection")

#Fit GLMM for CD8 cells
model <- glmer(num_pos_per_mm2 ~ treatment + (1 | animal),
data = ihc_data,
family = Gamma(link = "log"),
control = glmerControl(optimizer = "bobyqa"))

#plot(model)

#Estimated marginal means and pairwise comparisons
data_model <- emmeans(model, specs = pairwise ~ treatment, type = "response")$emmeans %>% as.data.frame()
contrast_results <- emmeans(model, specs = pairwise ~ treatment, adjust = "Holm")$contrasts %>%
summary(infer = TRUE) %>% as.data.frame()
contrast_results <- contrast_results %>%
  mutate(
    p_value = round(p.value, 4),
    sig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE            ~ "ns"
    )
  )
```



```{r}
plot_cd8_no_inf <- ggplot(data_model, aes(treatment, response)) +
geom_point(data = ihc_data, aes(treatment, num_pos_per_mm2, color = treatment),
position = position_jitterdodge(jitter.width = 0.3), alpha = 0.5, size = 3) +
geom_point(size = 3, color = "firebrick3", shape = 3) +
geom_errorbar(aes(ymin = response - SE, ymax = response + SE), color = "firebrick3", width = 0, linewidth = 0.5) +
theme_light() + ylab(expression("Positive cells per mm"^2)) + ggtitle("CD8 Cells") +
geom_text(data = contrast_results, aes(x = 1.5, y = 10, label = paste("p =", sig)), size = 4, vjust = -1) +
scale_y_log10()+
scale_color_manual(values = c("#84838B", "#84838B"))

plot_cd8_no_inf
```

## cas3 IHC Analysis

```{r}
#Load IHC data (cas3, infection group)
ihc_data <- read_excel(paste0(path, "Fig_S1.xlsx"), sheet = "S1H") %>%
filter(staining == "cas3" & infection == "infection")

#Fit GLMM for cas3 cells
model <- glmer(num_pos_per_mm2 ~ treatment + (1 | animal),
data = ihc_data,
family = Gamma(link = "log"),
control = glmerControl(optimizer = "bobyqa"))

#plot(model)

#Estimated marginal means and pairwise comparisons
data_model <- emmeans(model, specs = pairwise ~ treatment, type = "response")$emmeans %>% as.data.frame()
contrast_results <- emmeans(model, specs = pairwise ~ treatment, adjust = "Holm")$contrasts %>%
summary(infer = TRUE) %>% as.data.frame()
contrast_results <- contrast_results %>%
  mutate(
    p_value = round(p.value, 4),
    sig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE            ~ "ns"
    )
  )
```

## Plot: cas3 IHC (Infection Group)

```{r}
plot_cas3_inf <- ggplot(data_model, aes(treatment, response)) +
geom_point(data = ihc_data, aes(treatment, num_pos_per_mm2, color = treatment),
position = position_jitterdodge(jitter.width = 0.3), alpha = 0.5, size = 3) +
geom_point(size = 3, color = "firebrick3", shape = 3) +
geom_errorbar(aes(ymin = response - SE, ymax = response + SE), color = "firebrick3", width = 0, linewidth = 0.5) +
theme_light() + ylab(expression("Positive cells per mm"^2)) + ggtitle("cas3 Cells") +
geom_text(data = contrast_results, aes(x = 1.5, y = 10, label = paste("p =", sig)), size = 4, vjust = -1) +
scale_y_log10()+
scale_color_manual(values = c("#EE7600", "#EE7600"))

plot_cas3_inf
```
```{r}
#Load IHC data (cas3, no infection group)
ihc_data <- read_excel(paste0(path, "Fig_S1.xlsx"), sheet = "S1H") %>%
filter(staining == "cas3" & infection == "no infection")

#Fit GLMM for cas3 cells
model <- glmer(num_pos_per_mm2 ~ treatment + (1 | animal),
data = ihc_data,
family = Gamma(link = "log"),
control = glmerControl(optimizer = "bobyqa"))

#plot(model)

#Estimated marginal means and pairwise comparisons
data_model <- emmeans(model, specs = pairwise ~ treatment, type = "response")$emmeans %>% as.data.frame()
contrast_results <- emmeans(model, specs = pairwise ~ treatment, adjust = "Holm")$contrasts %>%
summary(infer = TRUE) %>% as.data.frame()
contrast_results <- contrast_results %>%
  mutate(
    p_value = round(p.value, 4),
    sig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE            ~ "ns"
    )
  )
```



```{r}
plot_cas3_no_inf <- ggplot(data_model, aes(treatment, response)) +
geom_point(data = ihc_data, aes(treatment, num_pos_per_mm2, color = treatment),
position = position_jitterdodge(jitter.width = 0.3), alpha = 0.5, size = 3) +
geom_point(size = 3, color = "firebrick3", shape = 3) +
geom_errorbar(aes(ymin = response - SE, ymax = response + SE), color = "firebrick3", width = 0, linewidth = 0.5) +
theme_light() + ylab(expression("Positive cells per mm"^2)) + ggtitle("cas3 Cells") +
geom_text(data = contrast_results, aes(x = 1.5, y = 10, label = paste("p =", sig)), size = 4, vjust = -1) +
scale_y_log10()+
scale_color_manual(values = c("#84838B", "#84838B"))

plot_cas3_no_inf
```

## Ki67 IHC Analysis

```{r}
#Load IHC data (Ki67, infection group)
ihc_data <- read_excel(paste0(path, "Fig_S1.xlsx"), sheet = "S1I") %>%
filter(staining == "Ki67" & infection == "infection")

#Fit GLMM for Ki67 cells
model <- glmer(num_pos_per_mm2 ~ treatment + (1 | animal),
data = ihc_data,
family = Gamma(link = "log"),
control = glmerControl(optimizer = "bobyqa"))

#plot(model)

#Estimated marginal means and pairwise comparisons
data_model <- emmeans(model, specs = pairwise ~ treatment, type = "response")$emmeans %>% as.data.frame()
contrast_results <- emmeans(model, specs = pairwise ~ treatment, adjust = "Holm")$contrasts %>%
summary(infer = TRUE) %>% as.data.frame()
contrast_results <- contrast_results %>%
  mutate(
    p_value = round(p.value, 4),
    sig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE            ~ "ns"
    )
  )
```

## Plot: Ki67 IHC (Infection Group)

```{r}
plot_Ki67_inf <- ggplot(data_model, aes(treatment, response)) +
geom_point(data = ihc_data, aes(treatment, num_pos_per_mm2, color = treatment),
position = position_jitterdodge(jitter.width = 0.3), alpha = 0.5, size = 3) +
geom_point(size = 3, color = "firebrick3", shape = 3) +
geom_errorbar(aes(ymin = response - SE, ymax = response + SE), color = "firebrick3", width = 0, linewidth = 0.5) +
theme_light() + ylab(expression("Positive cells per mm"^2)) + ggtitle("Ki67 Cells") +
geom_text(data = contrast_results, aes(x = 1.5, y = 10, label = paste("p =", sig)), size = 4, vjust = -1) +
scale_y_log10()+
scale_color_manual(values = c("#EE7600", "#EE7600"))

plot_Ki67_inf
```
```{r}
#Load IHC data (Ki67, no infection group)
ihc_data <- read_excel(paste0(path, "Fig_S1.xlsx"), sheet = "S1I") %>%
filter(staining == "Ki67" & infection == "no infection")

#Fit GLMM for Ki67 cells
model <- glmer(num_pos_per_mm2 ~ treatment + (1 | animal),
data = ihc_data,
family = Gamma(link = "log"),
control = glmerControl(optimizer = "bobyqa"))

#plot(model)

#Estimated marginal means and pairwise comparisons
data_model <- emmeans(model, specs = pairwise ~ treatment, type = "response")$emmeans %>% as.data.frame()
contrast_results <- emmeans(model, specs = pairwise ~ treatment, adjust = "Holm")$contrasts %>%
summary(infer = TRUE) %>% as.data.frame()
contrast_results <- contrast_results %>%
  mutate(
    p_value = round(p.value, 4),
    sig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE            ~ "ns"
    )
  )
```



```{r}
plot_Ki67_no_inf <- ggplot(data_model, aes(treatment, response)) +
geom_point(data = ihc_data, aes(treatment, num_pos_per_mm2, color = treatment),
position = position_jitterdodge(jitter.width = 0.3), alpha = 0.5, size = 3) +
geom_point(size = 3, color = "firebrick3", shape = 3) +
geom_errorbar(aes(ymin = response - SE, ymax = response + SE), color = "firebrick3", width = 0, linewidth = 0.5) +
theme_light() + ylab(expression("Positive cells per mm"^2)) + ggtitle("Ki67 Cells") +
geom_text(data = contrast_results, aes(x = 1.5, y = 10, label = paste("p =", sig)), size = 4, vjust = -1) +
scale_y_log10()+
scale_color_manual(values = c("#84838B", "#84838B"))

plot_Ki67_no_inf
```


## CD31 IHC Analysis

```{r}
#Load IHC data (CD31, infection group)
ihc_data <- read_excel(paste0(path, "Fig_S1.xlsx"), sheet = "S1J") %>%
filter(staining == "CD31" & infection == "infection")

#Fit GLMM for CD31 cells
model <- glmer(num_pos_per_mm2 ~ treatment + (1 | animal),
data = ihc_data,
family = Gamma(link = "log"),
control = glmerControl(optimizer = "bobyqa"))

#plot(model)

#Estimated marginal means and pairwise comparisons
data_model <- emmeans(model, specs = pairwise ~ treatment, type = "response")$emmeans %>% as.data.frame()
contrast_results <- emmeans(model, specs = pairwise ~ treatment, adjust = "Holm")$contrasts %>%
summary(infer = TRUE) %>% as.data.frame()
contrast_results <- contrast_results %>%
  mutate(
    p_value = round(p.value, 4),
    sig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE            ~ "ns"
    )
  )
```

## Plot: CD31 IHC (Infection Group)

```{r}
plot_CD31_inf <- ggplot(data_model, aes(treatment, response)) +
geom_point(data = ihc_data, aes(treatment, num_pos_per_mm2, color = treatment),
position = position_jitterdodge(jitter.width = 0.3), alpha = 0.5, size = 3) +
geom_point(size = 3, color = "firebrick3", shape = 3) +
geom_errorbar(aes(ymin = response - SE, ymax = response + SE), color = "firebrick3", width = 0, linewidth = 0.5) +
theme_light() + ylab(expression("Positive cells per mm"^2)) + ggtitle("CD31 Cells") +
geom_text(data = contrast_results, aes(x = 1.5, y = 10, label = paste("p =", sig)), size = 4, vjust = -1) +
scale_y_log10()+
scale_color_manual(values = c("#EE7600", "#EE7600"))

plot_CD31_inf
```
```{r}
#Load IHC data (CD31, no infection group)
ihc_data <- read_excel(paste0(path, "Fig_S1.xlsx"), sheet = "S1J") %>%
filter(staining == "CD31" & infection == "no infection")

#Fit GLMM for CD31 cells
model <- glmer(num_pos_per_mm2 ~ treatment + (1 | animal),
data = ihc_data,
family = Gamma(link = "log"),
control = glmerControl(optimizer = "bobyqa"))

#plot(model)

#Estimated marginal means and pairwise comparisons
data_model <- emmeans(model, specs = pairwise ~ treatment, type = "response")$emmeans %>% as.data.frame()
contrast_results <- emmeans(model, specs = pairwise ~ treatment, adjust = "Holm")$contrasts %>%
summary(infer = TRUE) %>% as.data.frame()
contrast_results <- contrast_results %>%
  mutate(
    p_value = round(p.value, 4),
    sig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE            ~ "ns"
    )
  )
```



```{r}
plot_CD31_no_inf <- ggplot(data_model, aes(treatment, response)) +
geom_point(data = ihc_data, aes(treatment, num_pos_per_mm2, color = treatment),
position = position_jitterdodge(jitter.width = 0.3), alpha = 0.5, size = 3) +
geom_point(size = 3, color = "firebrick3", shape = 3) +
geom_errorbar(aes(ymin = response - SE, ymax = response + SE), color = "firebrick3", width = 0, linewidth = 0.5) +
theme_light() + ylab(expression("Positive cells per mm"^2)) + ggtitle("CD31 Cells") +
geom_text(data = contrast_results, aes(x = 1.5, y = 10, label = paste("p =", sig)), size = 4, vjust = -1) +
scale_y_log10()+
scale_color_manual(values = c("#84838B", "#84838B"))

plot_CD31_no_inf
```


## Hif1a IHC Analysis

```{r}
#Load IHC data (Hif1a, infection group)
ihc_data <- read_excel(paste0(path, "Fig_S1.xlsx"), sheet = "S1K") %>%
filter(staining == "Hif1a" & infection == "infection")

#Fit GLMM for Hif1a cells
model <- glmer(dab_intensity ~ treatment + (1 | animal),
data = ihc_data,
family = Gamma(link = "identity"),
control = glmerControl(optimizer = "bobyqa"))

#plot(model)

#Estimated marginal means and pairwise comparisons
data_model <- emmeans(model, specs = pairwise ~ treatment, type = "response")$emmeans %>% as.data.frame()
contrast_results <- emmeans(model, specs = pairwise ~ treatment, adjust = "Holm")$contrasts %>%
summary(infer = TRUE) %>% as.data.frame()
contrast_results <- contrast_results %>%
  mutate(
    p_value = round(p.value, 4),
    sig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE            ~ "ns"
    )
  )
```

## Plot: Hif1a IHC (Infection Group)

```{r}
plot_Hif1a_inf <- ggplot(data_model, aes(treatment, emmean)) +
geom_point(data = ihc_data, aes(treatment, dab_intensity, color = treatment),
position = position_jitterdodge(jitter.width = 0.3), alpha = 0.5, size = 3) +
geom_point(size = 3, color = "firebrick3", shape = 3) +
geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), color = "firebrick3", width = 0, linewidth = 0.5) +
theme_light() + ylab(expression("Mean nucleus intensity per field of view")) + ggtitle("Hif1a Cells") +
geom_text(data = contrast_results, aes(x = 1.5, y = 0.2, label = paste("p =", sig)), size = 4, vjust = -1) +
scale_y_log10()+
scale_color_manual(values = c("#EE7600", "#EE7600"))

plot_Hif1a_inf
```
```{r}
#Load IHC data (Hif1a, no infection group)
ihc_data <- read_excel(paste0(path, "Fig_S1.xlsx"), sheet = "S1K") %>%
filter(staining == "Hif1a" & infection == "no infection")

#Fit GLMM for Hif1a cells
model <- glmer(dab_intensity ~ treatment + (1 | animal),
data = ihc_data,
family = Gamma(link = "identity"),
control = glmerControl(optimizer = "bobyqa"))

#plot(model)

#Estimated marginal means and pairwise comparisons
data_model <- emmeans(model, specs = pairwise ~ treatment, type = "response")$emmeans %>% as.data.frame()
contrast_results <- emmeans(model, specs = pairwise ~ treatment, adjust = "Holm")$contrasts %>%
summary(infer = TRUE) %>% as.data.frame()
contrast_results <- contrast_results %>%
  mutate(
    p_value = round(p.value, 4),
    sig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE            ~ "ns"
    )
  )
```

```{r}
plot_Hif1a_no_inf <- ggplot(data_model, aes(treatment, emmean)) +
geom_point(data = ihc_data, aes(treatment, dab_intensity, color = treatment),
position = position_jitterdodge(jitter.width = 0.3), alpha = 0.5, size = 3) +
geom_point(size = 3, color = "firebrick3", shape = 3) +
geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), color = "firebrick3", width = 0, linewidth = 0.5) +
theme_light() + ylab(expression("Positive cells per mm"^2)) + ggtitle("Hif1a Cells") +
geom_text(data = contrast_results, aes(x = 1.5, y = 0.2, label = paste("p =", sig)), size = 4, vjust = -1) +
scale_y_log10()+
scale_color_manual(values = c("#84838B", "#84838B"))

plot_Hif1a_no_inf
```

## RelA IHC Analysis

```{r}
#Load IHC data (RelA, infection group)
ihc_data <- read_excel(paste0(path, "Fig_S1.xlsx"), sheet = "S1L") %>%
filter(staining == "RelA" & infection == "infection")

#Fit GLMM for Hif1a cells
model <- glmer(dab_intensity ~ treatment + (1 | animal),
data = ihc_data,
family = Gamma(link = "identity"),
control = glmerControl(optimizer = "bobyqa"))

#plot(model)

#Estimated marginal means and pairwise comparisons
data_model <- emmeans(model, specs = pairwise ~ treatment, type = "response")$emmeans %>% as.data.frame()
contrast_results <- emmeans(model, specs = pairwise ~ treatment, adjust = "Holm")$contrasts %>%
summary(infer = TRUE) %>% as.data.frame()
contrast_results <- contrast_results %>%
  mutate(
    p_value = round(p.value, 4),
    sig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE            ~ "ns"
    )
  )
```

## Plot: RelA IHC (Infection Group)

```{r}
plot_RelA_inf <- ggplot(data_model, aes(treatment, emmean)) +
geom_point(data = ihc_data, aes(treatment, dab_intensity, color = treatment),
position = position_jitterdodge(jitter.width = 0.3), alpha = 0.5, size = 3) +
geom_point(size = 3, color = "firebrick3", shape = 3) +
geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), color = "firebrick3", width = 0, linewidth = 0.5) +
theme_light() + ylab(expression("Mean cell intensity per field of view")) + ggtitle("RelA Cells") +
geom_text(data = contrast_results, aes(x = 1.5, y = 0.1, label = paste("p =", sig)), size = 4, vjust = -1) +
scale_y_log10()+
scale_color_manual(values = c("#EE7600", "#EE7600"))

plot_RelA_inf
```
```{r}
#Load IHC data (RelA, no infection group)
ihc_data <- read_excel(paste0(path, "Fig_S1.xlsx"), sheet = "S1L") %>%
filter(staining == "RelA" & infection == "no infection")

#Fit GLMM for Hif1a cells
model <- glmer(dab_intensity ~ treatment + (1 | animal),
data = ihc_data,
family = Gamma(link = "identity"),
control = glmerControl(optimizer = "bobyqa"))

#plot(model)

#Estimated marginal means and pairwise comparisons
data_model <- emmeans(model, specs = pairwise ~ treatment, type = "response")$emmeans %>% as.data.frame()
contrast_results <- emmeans(model, specs = pairwise ~ treatment, adjust = "Holm")$contrasts %>%
summary(infer = TRUE) %>% as.data.frame()
contrast_results <- contrast_results %>%
  mutate(
    p_value = round(p.value, 4),
    sig = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE            ~ "ns"
    )
  )
```

```{r}
plot_RelA_no_inf <- ggplot(data_model, aes(treatment, emmean)) +
geom_point(data = ihc_data, aes(treatment, dab_intensity, color = treatment),
position = position_jitterdodge(jitter.width = 0.3), alpha = 0.5, size = 3) +
geom_point(size = 3, color = "firebrick3", shape = 3) +
geom_errorbar(aes(ymin = emmean - SE, ymax = emmean + SE), color = "firebrick3", width = 0, linewidth = 0.5) +
theme_light() + ylab(expression("Mean cell intensity per field of view")) + ggtitle("RelA Cells") +
geom_text(data = contrast_results, aes(x = 1.5, y = 0.1, label = paste("p =", sig)), size = 4, vjust = -1) +
scale_y_log10()+
scale_color_manual(values = c("#84838B", "#84838B"))

plot_RelA_no_inf
```

---

**Instructions:**
- Set the `path` variable if your files are not in your working directory.
- Make sure your Excel files and sheet names match those in the code.
- Make sure to check model diagnostics.


